Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-06-30 article.tex
Riaz and Li articles added

>>>>

Moreover, there are some other methods, such as the method proposed by Riaz et. al. which is a hybrid approach based on functional connectivity and deep learning to classify ADHD patients. This algorithm divides functional connectivities to different clusters and employs an Elastic Net to select the most discriminant features among the connectivities and the phenotypic information. Finally, a support vector machine will be trained as the classifier \cite{Riaz2020}. This method has shown an acceptable performance on some datasets and can be used for other diseases as well. Unlike our proposed method, this one is still focusing on time-based data such as functional connectivity.

Another eye-catching research is "Detecting Alzheimer’s disease based on 4D fMRI" by Li et. al. This method is empowered by coupling 3D-CNN with long short-term memory (LSTM) together. Similar to the latter algorithm, this one also tries to take advantage of both temporal and structural information inside the 4D images of fMRI. In brief, the mentioned method feeds each time-slice to a different CNNs to extract spatial features. Then the feature maps will be put into an LSTM to capture time-varying features. Subsequently, the output of the last layer will enter a fully-connected layer to do the classification \cite{Li2020}. Although this method is well-engineered, it still utilizes both spatial and temporal information. As mentioned earlier, our method will focus only on spatial data to find out about the potential of it in the task of classification.
